---
title: "Lab 00 - Hello IDS!"
author: "Peter McGrath"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter McGrath", "member 1", "member 2", 
           "member 3", "member 4"),
  github_username = c("pmcgrath735", "username 1", "username 2", 
                      "username 3", "username 4"), 
  colour = c("blue", "colour 1", "colour 2", 
             "colour 3", "colour 4"),
  hobby = c("Golf", "hobby 1", "hobby 2", 
            "hobby 3", "hobby 4"),
  favourite_number = c(9, NA, NA, NA, NA)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


*Bar Graph showing each usernames favourite number.*

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub Username", 
          y = "Favourite Number",
          title = "Favourite number and colour for each Username")
```

*This changes the names of both axis as well as title.*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Put each hobby into a category eg. sports, music, art etc.*
